Scalar Items in Embedded Position: {A}n Experimental Revisit

### 2012-11-08 text/paper/paper2.tex
small changes results parts

% \includegraphics[width=5cm]{../pictures/paper/ReadingsGE.pdf}
\label{fig:JudgementPercentagesGE}
}
\caption[Optional caption for list of figures]{Response type
  frequencies for target conditions}
\label{fig:JudgementPercentages}
\end{figure}
%
Participants mostly gave judgments indicating literal or local
readings. Judgments compatible with a global reading were seldom
obtained. In the \as-conditions participants made hardly any errors,
whereas the amount of errors was considerably larger in the
\es-conditions.

In the \as-conditions (see Figure~\ref{fig:JudgementPercentagesAE})
judgments were consistent with literal readings in 65.0\% of the
trials with neutral prosody and in 67.5\% of the trials with accented
prosody.\dn{IMPORTANT: Figure contains different numbers (even if
  rounded)! Fabian, did you exclude the 3 bad performers when you
  obtained this data?} The number of global readings was very low,
with 1.6\% of the neutral and 0.8\% of the accented trials
(corresponding to a total of 3 answers across all trials). Judgments
indicating local readings were given in 22.0\% of both the neutral and
accented trials. In the \es-conditions (see
Figure~\ref{fig:JudgementPercentagesGE}) judgments consistent with
literal readings were given in 47.2\% and 44.7\% of the trials with
neutral and accented prosody respectively. Global readings were
observed in 0.8\% of the trials in both the neutral and the accented
condition. Judgments indicating local readings were given in 22.8\% of
the neutral and 27.6\% of the accented trials.

In order to test wether local readings exist we tested whether the
number of local responses in each condition was higher than expected
by chance. Local responses had to be given on the last position in
each trial. If local readings didn't exist we would expect
participants, who reached the last position (ie. who did not abort the
trial prior to the last position) to give local judgments not more
often than expected by chance. On the last position two responses were
possible. One was compatible with a local reading the other was
not. Therefore, we would expect 50\% local responses by chance. As it
turns out local responses were given significantly more often than
50\% in all target conditions (all Bonferoni corrected p<.05). Note
that this finding cannot be explained by some kind of general response
bias on the last position since local readings required a yes-judgment
in the \es-conditions but a no-judgment in the \as-conditions.

@@

Participants' judgments are depicted in Figures \ref{Fig:EC_judgments} and 
\ref{Fig:LC_judgments}. Judgments were coded as \ec or as \lc if they were as expected
under one of these readings, and as "other" if they were not. The distributions 
of readings thus coded is illustrated in Figure \ref{fig:response-type-freque-TRF}. 
Overall, participants mainly gave answers corresponding to the \lc-reading. Moreover,
the preference for this reading was constrained by prosody. When prosody supported 
a dispreferred \ec-reading, the number of \lc-decisions was decreased. The number 
of erroneous answers did not differ between the single conditions. Finally, the
availability of readings within a sequence did not yield any significant effects.

In both \lc- and \ec-sequences, the number of \lc-answers was highest when this reading
was supported by prosodic phrasing (i.e. 77\%  and 76\% , respectively), and a bit lower
with neutral prosody (69\%  and 63\% ). This clearcut advantage decreased when prosodic
phrasing supported the \ec-reading (52\%  vs. 56\% ).

In order to test statistically whether prosodic phrasing and the sequential ordering 
had an effect on the number of \lc choices, log-linear models with the factors
{\it Reading}, {\it Prosody}, {\it Sequence}, {\it Item}, and {\it Participant} were included.

>>>>

% \includegraphics[width=5cm]{../pictures/paper/ReadingsGE.pdf}
\label{fig:JudgementPercentagesGE}
}
\caption[Optional caption for list of figures]{Response type
  frequencies for target conditions}
\label{fig:JudgementPercentages}
\end{figure}
%
Participants mostly gave judgments indicating literal or local
readings. Judgments compatible with a global reading were seldomly
obtained. In the \as-conditions (see Figure~\ref{fig:JudgementPercentagesAE}),
judgments were consistent with literal readings in 65.0\% of the
trials with neutral prosody and in 67.5\% of the trials with accented
prosody.\dn{IMPORTANT: Figure contains different numbers (even if
  rounded)! Fabian, did you exclude the 3 bad performers when you
  obtained this data?} Judgments indicating local readings were given 
  in 22.0\% of both the neutral and accented trials. Global readings 
occurred in 1.6\% of the neutral and 0.8\% of the accented trials
(corresponding to a total of 3 answers across all trials).  
In the \es-conditions (see Figure~\ref{fig:JudgementPercentagesGE}) 
judgments consistent with literal readings were given in 47.2\% and 
44.7\% of the trials with neutral and accented prosody, respectively. 
Judgments indicating local readings were given in 22.8\% of
the neutral and 27.6\% of the accented trials. Global readings were
observed in 0.8\% of the trials in both the neutral and the accented
condition. 
As for the number of erroneous decisions, a discrepancy between 
\as-conditions and \es-conditions was observed: In the former, 
participants made hardly any errors, while in the latter, the amount 
of errors was considerably larger.

In order to test wether local readings occurred reliably, we tested whether the
number of local responses in each condition was higher than expected
by chance. Local responses had to be given on the last position in
each trial. If local readings didn't exist we would expect
participants, who reached the last position (ie. who did not abort the
trial prior to the last position) to give local judgments not more
often than expected by chance. On the last position two responses were
possible. One was compatible with a local reading the other was
not. Therefore, we would expect 50\% local responses by chance. As it
turns out local responses were given significantly more often than
50\% in all target conditions (all Bonferoni corrected p<.05). Note
that this finding cannot be explained by some kind of general response
bias on the last position since local readings required a yes-judgment
in the \es-conditions but a no-judgment in the \as-conditions.

@@

Participants' judgments are depicted in Figures \ref{Fig:EC_judgments} and 
\ref{Fig:LC_judgments}. Judgments were coded as \ec or as \lc if they were as expected
under one of these readings, and as "other" if they were not. The distributions 
of readings thus coded is illustrated in Figure \ref{fig:response-type-freque-TRF}. 
Overall, participants mainly gave answers corresponding to the \lc-reading (65\%). 
Moreover, the preference for this reading was constrained by prosody. When prosody 
supported a dispreferred \ec-reading, the number of \lc-decisions was decreased. In both 
\lc- and \ec-sequences, the number of \lc-answers was highest when this reading
was supported by prosodic phrasing (i.e. 77\%  and 76\%, respectively), and a bit lower
with neutral prosody (69\%  and 63\%). This clearcut advantage decreased when prosodic
phrasing supported the \ec-reading (52\%  vs. 56\%). The number 
of erroneous answers did not differ between the single conditions. Finally, the
availability of readings within a sequence did not yield any significant effects.

In order to test statistically whether prosodic phrasing and sequential ordering 
had an effect on the number of \lc choices, log-linear models with the factors
{\it Reading}, {\it Prosody}, {\it Sequence}, {\it Item}, and {\it Participant} were included.
